% -- \include{slbdecays.tex}
% ======================================================================

%\cleardoublepage

\section{Semileptonic $B$ decays}
\label{sec:slbdecays}

This section contains our averages for semileptonic $B$~meson decays,
{\it i.e.}, decays of the type $B\to X\ell\nu_\ell$, where $X$ is a
hadronic system, $\ell$ a charged lepton and $\nu_\ell$ its corresponding
neutrino. Unless otherwise stated, $\ell$ stands for an electron
\emph{or} a muon, lepton universality is assumed, and both charge
conjugate states are included. Some averages assume isospin symmetry
and this will be explicitly mentioned at every instance.

The averages are organized by the flavour changing transition
(the CKM-favoured $b\to c$ transition and the CKM-suppressed $b\to u$
transition) and by the experimental definition of the hadronic
$X$~system. Measurements which are sensitive to only a specific
hadronic state ($X=D,D^*,\pi,\dots$) are called \emph{exclusive} while
analyses that measure all hadronic states within a given region of
phase space are \emph{inclusive}. The principal reason why semileptonic
$B$~decays are studied in experiments is the determination of the CKM
matrix element magnitudes $|V_{cb}|$ and $|V_{ub}|$. The averages in
the different subsections thus focus very much on these two
fundamental parameters of the Standard Model. In the last subsection,
we discuss semileptonic $B$~decays with a $\tau$-lepton. These
decays are relevant to the search for physics beyond the Standard
Model, {\it e.g.}, in the context of the type II
Two-Higgs-Doublet-Model (2HDM).

The technique for obtaining the averages follows the general HFAG
procedure (Sect.~\ref{sec:method}) unless otherwise stated. More
information on the averages, in particular the common input parameters
is available on the HFAG semileptonic webpage:

\centerline{\tt http://www.slac.stanford.edu/xorg/hfag/semi/pdg14/}

% ======================================================================

%% \clearpage

% ======================================================================
% Common set of input parameters

%%%commented out 2-Aug-2010 by AJS
%%%\input{slbdecays/common.tex}

% ======================================================================
% Exclusive CKM-favoured decays
\input{slbdecays/exclusiveclnu.tex}

%
% ======================================================================
% Inclusive CKM-favoured decays
\input{slbdecays/inclusiveclnu.tex}


% ======================================================================
% Exclusive CKM-suppressed decays
\input{slbdecays/exclusiveulnu.tex}

%
% ======================================================================
% Inclusive CKM-suppressed decays
\input{slbdecays/inclusiveulnu.tex}

%
% ======================================================================
% B --> D(*) tau nu_tau
\input{slbdecays/btodtaunu.tex}


%
% ======================================================================
%
