\mysection{$B$ decays to charmless final states}


\label{sec:rare}

%The aim of this section is to provide the branching fractions, polarization 
This section provides the branching fractions, polarization 
fractions, the partial rate asymmetries ($A_{\CP}$) and other observables of charmless 
$B$ decays.
The order of entries in the Tables correspond to that in the PDG, and the quoted RPP numbers correspond to the PDG numbers of the corresponding branching fractions.
The asymmetry is defined as 
$A_{\CP} = \frac{N_{\Bbar} -N_B}{N_{\Bbar} +N_B}$, where $N_{\Bbar}$ 
and $N_B$ are respectively number of $\Bzb/\Bm$ and $\Bz/\Bp$ decaying
into a specific final state.
Four different $B$ decay categories are considered: 
charmless mesonic, baryonic, radiative and leptonic. We also include
measurements of $B_s$ decays.
Measurements supported with  written documents are accepted in  
the averages; written documents include journal papers, 
conference contributed papers, preprints or conference proceedings.  
Results from  $A_{\CP}$ measurements  obtained from time-dependent analyses 
are listed and described in Sec.~\ref{sec:cp_uta}.

%So far all
Most of the branching fractions from \babar\ and Belle assume equal production 
of charged and neutral $B$ pairs.  The best measurements to date show that this
is still a reasonable approximation (see Sec.~\ref{sec:life_mix}).
For branching fractions, we provide either averages or the most stringent
90\% confidence level (CL) upper limits.  If one or more experiments have
measurements with $>\!\!4 \sigma$ for a decay channel, all available central values
for that channel are used in the averaging.  We also give central values
and errors for cases where the significance of the average value is at
least $3 \sigma$, even if no single measurement is above $4 \sigma$. 
Since a few decay modes are sensitive to the contribution of
new physics and the current experimental upper limits are not far from the 
Standard Model expectation, we provide the combined upper limits or
averages in these cases.
Their upper limits can be estimated assuming that the errors are 
Gaussian.  For $A_{\CP}$ we provide averages in all cases.  

Our averaging is performed by maximizing the likelihood,
%\begin{eqnarray}
   $\displaystyle {\mathcal L} = \prod_i {\mathcal P}_i(x),$  
%\end{eqnarray}
where ${\mathcal P_i}$ is the probability density function (PDF) of the
$i^{\rm th}$  measurement, and $x$ is the branching fraction or $A_{CP}$.
The PDF is modeled by an asymmetric Gaussian function with the measured
central value as its mean and the quadratic sum of the statistical
and systematic errors as the standard deviations. The experimental
uncertainties are considered to be uncorrelated with each other when the 
averaging is performed. No error scaling is applied when the fit $\chi^2$ is 
greater than 1 since we believe that tends to overestimate the errors
except in cases of extreme disagreement (we have no such cases).
% EB: we need to decide what to do with the B -> Xs gamma measurement. In the previous paper there was a dedicated section
%%One exception to consider the correlated systematic errors is the inclusive
%%$B\to X_s\gamma$ mode, which is sensitive to physics beyond the Standard Model.
%%In this update, we have included new measurements from both Belle and \babar\
%%to perform the average. The detail is  
%%described  in Sec. ~\ref{sec:btosg}. 

At present, we have measurements of more than 500 decay modes, reported in
hundreds of 
%about 300
papers. Because the number of references is so large, we do
not include them with the tables shown here but the full set of
references is available from active gifs at the 
``2014'' link on 
the rare decays HFAG web page: {\tt http://www.slac.stanford.edu/xorg/hfag/rare/index.html}.
The largest improvement since the last report has come from the inclusion of a
variety of new measurements from the LHC, especially LHCb.  The
measurements of $B_s$ decays are particularly noteworthy.

Sections \ref{sec:rare-charmless} and \ref{sec:rare-bary} provide compilations of branching fractions of $\Bz$ and $\Bp$ to mesonic and baryonic charmless final states, respectively, 
while Sec.~\ref{sec:rare-lb} gives branching fractions of $\Lambda_b$ decays.
In Sec.~\ref{sec:rare-bs} and \ref{sec:rare-radll} different observables of interest are detailed in addition to branching fractions: in the former for \Bs-meson charmless decays, and in the latter for leptonic and radiative \Bz\ and \Bp\ meson decays, including processes in which the photon yields a pair of charged of neutral leptons. This section also contains limits from searches for lepton-number-violating decays.
Finally, Sec.~\ref{sec:rare-acp} and \ref{sec:rare-polar} give \CP asymmetries and results of polarization measurements, respectively, in different $b$-hadron charmless decays.


\mysubsection{Mesonic decays of \Bz and \Bp\ mesons}
\label{sec:rare-charmless}

This section provides branching fractions of charmless mesonic decays:
Tables~\ref{tab:charmless_BpFirst} to \ref{tab:charmless_BpLast} for \Bp\
and Tables~\ref{tab:charmless_BdFirst} to
\ref{tab:charmless_BdLast}
for \Bz\ mesons.
The tables are separated according to the presence or absence of kaons in the final state. 
Finally, Table~\ref{tab:charmless_Ratio} details several relative branching fractions of \Bz decays.

\input{rare/charmless}
\vspace{-0.8cm}


\mysubsection{Baryonic decays of \Bz and \Bp\ mesons}
\label{sec:rare-bary}

This section provides branching fractions of charmless baryonic decays of \Bz and \Bp\ mesons in Tables~\ref{tab:bary_Bp} and~\ref{tab:bary_Bz}, respectively. Relative branching fractions are given in Table~\ref{tab:bary_Ratio}.

\input{rare/bary}
\clearpage


\mysubsection{Decays of \b baryons}
\label{sec:rare-lb}

A compilation of branching fractions of $\Lb$ baryon decays is given in Table~\ref{tab:bbaryons_Lb}. Table~\ref{tab:bbaryons_LbPartialBF} provides the partial branching fractions of $\Lb\to\Lambda\mup\mun$ decays.

\input{rare/bbaryons}

\clearpage

\mysubsection{Decays of \Bs mesons}
\label{sec:rare-bs}

Tables~\ref{tab:Bs_BF} and~\ref{tab:Bs_BF_rel} detail branching fractions and relative branching fractions of \Bs meson decays, respectively. Tables~\ref{tab:Bs_PartBF} to~\ref{tab:Bs_A9} give different observables for $\Bs\to\phi\mup\mun$ decays in bins of the dimuon invariant mass.

\input{rare/bs}

\clearpage

\mysubsection{Radiative and leptonic decays of \Bz and \Bp\ mesons}
\label{sec:rare-radll}

This section gives different observables for leptonic and radiative \Bz\ and \Bp\ meson decays, including processes in which the photon yields a pair of charged of neutral leptons. Tables~\ref{tab:radll_Bp}, \ref{tab:radll_Bz} and~\ref{tab:radll_B} provide compilations of branching fractions of \Bp, \Bz, and $\Bpm/\Bz$ admixture, respectively.
Table~\ref{tab:radll_lep} contains branching fractions of leptonic and radiative-leptonic $\Bp$ and $\Bz$ decays. It is followed by Tabs~\ref{tab:radll_rel} and~\ref{tab:radll_gluon}, which give relative branching fractions of $\Bp$ decays and a compilations of inclusive decays, respectively. The next two tables detail isospin asymmetries: Table~\ref{tab:radll_AI} contains overall measurements, and~\ref{tab:radll_AI_Kll} measurements in bins of dimuon invariant mass, $q^2$, bins for $\B\to K^{(\ast)}\ell^+\ell^-$ decays. Tables~\ref{tab:radll_AFB_Kll} and~\ref{tab:radll_FL_Kll} detail measurements of the forward-backward asymmetry and the fraction of longitudinal polarization, respectively, in $\B\to K^{(\ast)}\ell^+\ell^-$ decays in bins of $q^2$. Finally, Table~\ref{tab:radll_Aud} quotes the LHCb measurement of photon polarization via the Up-Down asymmetry in $B^+ \to K^+ \pi^- \pi^+ \gamma$ decays.

\input{rare/radll}

\clearpage

\mysubsection{Charge asymmetries in \b-hadron decays}
\label{sec:rare-acp}

This section contains, in Tables~\ref{tab:acp_Bp} to~\ref{tab:acp_Lb}
compilations of \CP\ asymmetries in decays of different \b-hadrons: \Bp, \Bz
mesons, $\Bpm/\Bz$ admixtures, \Bs mesons and finally \Lb baryons.
Measurements of time-dependent \CP\ asymmetries are not listed here but are
discussed in Sec.~\ref{sec:cp_uta}.
In addition, we do not attempt to include the model-independent studies of
$CP$ violation across the phase space of the three body decays $\Bp \to
\Kp\Km\Kp$, $\Kp\pim\pip$, $\Kp\Km\pip$ and $\pip\pim\pip$, where large
effects have been observed by LHCb~\cite{Aaij:2013sfa,Aaij:2013bla,Aaij:2014iva}.
The results, in terms of $CP$ asymmetries of quasi-two-body final states, of
model-dependent analyses, and of the $CP$ asymmetries for the inclusive
three-body final states, are however included.

\input{rare/acp}
\clearpage

\mysubsection{Polarization measurements in \b-hadron decays}
\label{sec:rare-polar}

In this section, compilations of polarization measurements in \b-hadron decays
are given. Tables~\ref{tab:polar_Bp} (\ref{tab:polar_Bz}) detail measurements
of the longitudinal fraction, $f_L$, in \Bp\ (\Bz) decays, and
Tables~\ref{tab:polar_BpAng} (\ref{tab:polar_BzAng}) the results of the full
angular analyses of $\Bp$ (\Bz) $\to\phi\Kstar$ decays. 
Table~\ref{tab:polar_BzAng1430} gives results of the full angular analysis of
$\Bz\to\phi K_2^{\ast 0}(1430)$ decays. 
Tables~\ref{tab:polar_Bs} to~\ref{tab:polar_BsAng2} detail quantities of \Bs decays: $f_L$ measurements, and observables from full angular analyses of decays to $\phi\phi$ and $\phi\Kstarzb$.

\input{rare/polar}

